---
title: "Cost-Benefit Analysis of Urban Forest"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---

```{r, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
# install packags and library
# install.packages("leaflet")
library(leaflet)
```

<style type="text/css"> .sidebar { overflow: auto; } </style>

Introduction {.storyboard}
=========================================
### Cost Benefit Analysis of developing Urban Forest in Phoenix, AZ. 
```{r}
leaflet() %>%
  addTiles(options = providerTileOptions(minZoom = 8, maxZoom = 10)) %>%
  addMarkers(lng=-112.0740, lat=33.4484, popup="City Center Phoenix, AZ")
```

***

**Location**: Phoenix, AZ -- State Capital of Arizoan and Fifth most populous ciy in the United States.    
**Objectives**: Increase Urban forest to offset the Carbon-Di-Oxide (CO2) generated by air travel by providing Cost-Beneefit analysis of five most comman urban species in the area.    
**Data Used**: Cost and Benefit of each species for a span 30 years.    
**Process**: Investigate the number of trees needed to offest the CO2 generated by a flight. Then navigate through details of cost and benefit provided by these trees while presenting the user with Net Present Value of the tree investement. 

Analysis {.storyboard}
=========================================


### Carbon generated by flights and Trees needed to offset the carbon


```{r}
## insert widget for user input


## insert widget for tree selection by the user from the list provided
```

*** 


### Details of cost and benefit of Properly installing a tree

```{r}

```

*** 

### Details of cost and benefit of conveniently installing a tree

```{r}

```

***

### Net present Value of Cost Benefit analysis 

```{r}

```
