---
title: "Cost-Benefit Analysis of Urban Forest"
output: 
  flexdashboard::flex_dashboard:
    storyboard: false
    social: menu
    source: embed
---

```{r, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
# install packags and library
# install.packages("leaflet")
#install.packages("flexdashboard")
#install.packages("shiny")

library(shiny)
library(flexdashboard)
library(leaflet)
```

<style type="text/css"> .sidebar { overflow: auto; } </style>

Introduction {.storyboard}
=========================================
### Cost Benefit Analysis of developing Urban Forest in Phoenix, AZ. 
```{r}
leaflet() %>%
  addTiles(options = providerTileOptions(minZoom = 8, maxZoom = 10)) %>%
  addMarkers(lng=-112.0740, lat=33.4484, popup="City Center Phoenix, AZ")
```

***

**Location**: Phoenix, AZ -- State Capital of Arizoan and Fifth most populous ciy in the United States.    
**Objectives**: Increase the Urban forest to offset the Carbon-Di-Oxide (CO2) generated by air travel by providing Cost-Beneefit analysis of five most comman urban tree species in the area.    
**Data Used**: Cost and Benefit of each of those species for a span 30 years.    
**Process**: Investigate the number of trees needed to offest the CO2 generated by a flight. Then navigate through details of cost and benefit provided by these trees while presenting the user with Net Present Value of the tree investement. 

Select Carbon Generation to offset {data-orientation=rows}
=========================================


### Select a flight to calculate carbon generation.

Sidebar {.sidebar}
-------------------------------------
```{r}
## insert widget for user input


fluidPage(
  # Copy the line below to make a set of radio buttons
  radioButtons("radio", label = h3("Select an appropriate round trip flight"),
    choices = list("Cross Counrty Flight (Six Hours Flight)" = 1, 
                   "Same Sector Flight (Three Hours Flight) " = 2, 
                   "Same Sector shorter flight ( Two hours Flight)" = 3), 
    selected = 1),
  
 # hr(),
 # fluidRow(column(3, verbatimTextOutput("value")))
)

## insert widget for tree selection by the user from the list provided
fluidPage(
  # Copy the line below to make a set of radio buttons
  radioButtons("radio", label = h3("Select the type of tree to offset carbon"),
    choices = list("Mesquite" = 1, 
                   "Blue Palo Verde " = 2, 
                   "Aleppo Pine" = 3,
                   "Chinese Elm" = 4, 
                   "Plao Brea" = 5), 
    selected = 1),
  
 # hr(),
 # fluidRow(column(3, verbatimTextOutput("value")))
)

```

Outputs
-------------------------------------

### Number of trees needed to offset the carbon

```{r}

```




*** 
Analysis {.storyboard}
=========================================


### Details of cost and benefit of Properly installing a tree

```{r}

```

*** 

### Details of cost and benefit of conveniently installing a tree

```{r}

```

***

### Net present Value of Cost Benefit analysis 

```{r}

```
